\documentclass{article}

\usepackage[letterpaper, margin=1in]{geometry} % Set page layout
\usepackage{titlesec} % Customize section titles
\usepackage{enumitem} % Customize itemize environment
\usepackage{hyperref} % Create hyperlinks
\usepackage{xcolor} % Define custom colors
\usepackage{parskip} % Add spacing between paragraphs
\usepackage{fontspec} % Specify fonts
\usepackage{lipsum} % For generating dummy text

% Define custom colors
\definecolor{darkblue}{RGB}{0,0,139}
\definecolor{gray}{RGB}{128,128,128}

% Set fonts
\setmainfont{Arial}
\setmonofont{Courier New}

% Customize section titles with numbers
\titleformat{\section}{\clearpage\large\bfseries\color{darkblue}}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\color{darkblue}}{\thesubsection}{1em}{}
\renewcommand{\thesection}{\arabic{section}} % Number sections with Arabic numerals
\renewcommand{\thesubsection}{\Roman{subsection}} % Number subsections with Roman numerals

\begin{document}

% Section Objectives
\section{Objectives}
\begin{enumerate}
    \item To create a user-friendly platform for listing and discovering used books for sale or exchange.
      \begin{enumerate}
          \item Implement advanced search and recommendation algorithms to help discover books on their preferences, location etc.
          \item Encourage both individual users and bookstores to use the platform regularly.
      \end{enumerate}
    \item To implement blockchain technology for secure and transparent transactions.
      \begin{enumerate}
          \item Explore blockchain platforms (e.g., Ethereum, Hyperledger) and enhance security and tranceparency.
          \item Implement blockchain for ensuring data integrity
      \end{enumerate}
    \item To develop AI models for personalized book recommendations and efficient book searches.
      \begin{enumerate}
          \item Implement collaborative filtering algorithms.
      \end{enumerate}
    \item To provide a centralized hub for users to manage their book transactions and interactions.
      \begin{enumerate}
          \item Create user profiles with transaction history.
          \item Incorporate a messaging system for user interactions.
      \end{enumerate}
    \item To offer accessibility and scalability, enabling users to access the platform from various devices.
    \item Enhance geographic Targeting
      \begin{enumerate}
       \item location based services to provide users with accurate book listings in their vicinity
      \end{enumerate}
       \item Encourage Book Exchanges
      \begin{enumerate}
          \item Foster sense of cost effective book sharing
         \item Facilitate fair trade terms
      \end{enumerate}
  \end{enumerate}

\end{document}
