\documentclass{article}

\usepackage[letterpaper, margin=1in]{geometry} % Set page layout
\usepackage{titlesec} % Customize section titles
\usepackage{enumitem} % Customize itemize environment
\usepackage{hyperref} % Create hyperlinks
\usepackage{xcolor} % Define custom colors
\usepackage{parskip} % Add spacing between paragraphs
\usepackage{fontspec} % Specify fonts
\usepackage{lipsum} % For generating dummy text

% Define custom colors
\definecolor{darkblue}{RGB}{0,0,139}
\definecolor{gray}{RGB}{128,128,128}

% Set fonts
\setmainfont{Arial}
\setmonofont{Courier New}

% Customize section titles with numbers
\titleformat{\section}{\clearpage\large\bfseries\color{darkblue}}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\color{darkblue}}{\thesubsection}{1em}{}
\renewcommand{\thesection}{\arabic{section}} % Number sections with Arabic numerals
\renewcommand{\thesubsection}{\Roman{subsection}} % Number subsections with Roman numerals

\begin{document}

% Title Page
\begin{titlepage}
    \centering
    \vspace*{\fill}
    \Huge\textbf{Project Proposal: Comprehensive Used Book Sale Exchange Solution}\par
    \vspace{1cm}
    \Large\textbf{Group 2}\par
    \vspace{1cm}
    \large\textbf{Date}\par
    \vspace*{\fill}
\end{titlepage}

\newpage
% Declaration
\begin{titlepage}
    \centering
    \vspace*{\fill}
    \Huge\textbf{Declaration}\par
    \vspace{1cm}
    \large
    We declare that this project proposal is our original work and has not been submitted elsewhere.\par
    \vspace{1cm}
    \large\textbf{Signature:} \underline{\hspace{6cm}}\par
    \vspace{1cm}
    \large\textbf{Date:} \underline{\hspace{3cm}}\par
    \vspace*{\fill}
\end{titlepage}

\newpage
% Table of Contents
\tableofcontents

\newpage
\section{Introduction}
\subsection{Introduction}
Your introduction content goes here.

\newpage
\subsection{Objectives}
\begin{enumerate}
    \item To create a user-friendly platform for listing and discovering used books for sale or exchange.
      \begin{enumerate}
          \item Implement advanced search and recommendation algorithms to help discover books on their preferences, location etc.
          \item Encourage both individual users and bookstores to use the platform regularly.
      \end{enumerate}
    \item To implement blockchain technology for secure and transparent transactions.
      \begin{enumerate}
          \item Explore blockchain platforms (e.g., Ethereum, Hyperledger) and enhance security and tranceparency.
          \item Implement blockchain for ensuring data integrity
      \end{enumerate}
    \item To develop AI models for personalized book recommendations and efficient book searches.
      \begin{enumerate}
          \item Implement collaborative filtering algorithms.
      \end{enumerate}
    \item To provide a centralized hub for users to manage their book transactions and interactions.
      \begin{enumerate}
          \item Create user profiles with transaction history.
          \item Incorporate a messaging system for user interactions.
      \end{enumerate}
    \item To offer accessibility and scalability, enabling users to access the platform from various devices.
    \item Enhance geographic Targeting
      \begin{enumerate}
       \item location based services to provide users with accurate book listings in their vicinity
      \end{enumerate}
       \item Encourage Book Exchanges
      \begin{enumerate}
          \item Foster sense of cost effective book sharing
         \item Fcilitate fair trade terms
      \end{enumerate}
  \end{enumerate}

\newpage
\subsection{Benefits of this Research}
\begin{enumerate}
    \item Using technologies like blockchain and decentralized data stores enhances user control, privacy, and security. There's less reliance on a centralized entity, reducing the risk of data breaches and ensuring trust in the system.
     \item Blockchain's encryption and decentralization features provide robust security for user data, reducing the risk of hacking or unauthorized access.
     \item You can use smart contracts to automate book exchanges, ensuring trust between parties and reducing the need for intermediaries.
     \item Transactions and book ownership records are stored on the blockchain, making them tamper-resistant and ensuring the provenance of books.
     \item Affordability: Users can access books at a lower cost compared to buying new ones, promoting affordability and accessibility to a broader audience.
     \item By extending the life cycle of books, the platform promotes sustainability by reducing the environmental impact associated with book production.
     \item Access to rare books: Users can find rare and out-of-print books, fostering a sense of excitement and discovery among book enthusiasts.
     \item AI algorithms can recommend books based on users' preferences and reading history, making it easier to discover new books tailored to individual interests.
     \item The platform can build a community of book lovers who share and exchange their passion for reading, connecting people with similar interests and encouraging knowledge sharing.
     \item Students, researchers, and lifelong learners can find affordable textbooks and references, making the platform a valuable educational resource.
     \item Users can access literature from different cultures and regions, promoting cultural exchange and fostering diversity.
     \item Open Access to Information: The platform aligns with open access principles, making knowledge and literature available without restrictive barriers.
     \item Local book exchange: The platform can facilitate both local book exchanges, connecting users with different geographic locations.
     \item The continuous supply of reading materials encourages lifelong learning, benefiting users of all ages.
     \item Students, professionals, and researchers can access books relevant to their studies and careers.
     \item Users take control of their reading choices and preferences, fostering a sense of ownership and responsibility within the community.
   \end{enumerate}

\newpage
\section{Background}
\subsection{Background}
Provide background information on your research topic.

\newpage
\subsection{Review on the Existing System}
We have conducted a comprehensive evaluation of the existing used books exchange websites. Those websites are aiming to provide a detailed overview of their features, performance, and user experience. This review serves as a foundation for our proposal to enhance and optimize the system to meet the evolving needs of our users. The mostly existing systems are focused on E-commerce or Cataloging, with limited emphasis on a comprehensive bookshop management system.

Common observations of some existing systems are as follows:
\begin{itemize}
    \item User interfaces vary in terms of simplicity and complexity.
    \item Integration with book databases and APIs is common for data retrieval and management.
\end{itemize}

Here's an overview of some of the globally existing websites:

\subsubsection{Amazon}
Amazon is a popular online Web-App that offers both new and used books for sale through third-party sellers. Users can find a wide selection of used books in various conditions. It offers a vast collection of books and a user-friendly interface. This system has several subcategories that the books are classified by department, format, author, promotions, prizes, languages, etc. The user rating and book description part of amazon.com are one of the best features, as it allows users to make an informed decision before purchasing a book. 
However, the disadvantages of this website are,
1. E-commerce focus
2. Limited transparency
3.lack of personalization
4. High transaction cost

\subsubsection{Goodreads}
Goodreads primarily serves as a social platform for readers, also some users may offer books for trade or giveaway in discussion forums. This includes details about authors, publication information, and user-generated content. The site allows users to set and track reading goals for the year, which is a great feature for people who like to challenge themselves to read more. It allows users to create virtual bookshelves, rate books, and connect with other readers. However, disadvantages of this are,
1. Limited transaction capabilities
2. Incomplete listings
3. Complex selling process

\subsubsection{AbeBooks}
AbeBooks is a well-established online marketplace for books, including new, used, rare, and out-of-print versions of books. Many independent sellers and bookstores list their inventory on AbeBooks, which means you can find books that may not be available on mainstream platforms. This website's interface is user-friendly, and sellers on AbeBooks typically provide detailed descriptions of the book's condition, edition, etc., as well as international shipping options. This helps buyers make informed decisions. The website consists of rare or antique books, often including first editions and signed copies. Disadvantages of using this are,
1. Limited free listings
2. Commercial nature

Here's an overview of some of the locally existing websites:

\subsubsection{Bookberry.lk}
Bookberry is an online website that offers to sell used books online. Even though not overly famous across Sri Lanka gives the facility to bank deposit or cash on delivery option for buyers. Disadvantages are that it doesn't contain a large collection of books and user interfaces are not friendly. 

\subsubsection{UsedBooks.lk}
UsedBooks.lk is an online marketplace for books where you can find used and rare books used by independent traders around Sri Lanka for sale.
Website contains detailed descriptions on the book's condition and photos uploaded by the seller. They also have various categories of books but the drawback is that since the books aren't categorized correctly the buyer finds trouble in sorting through the catelog looking for the book he wants. Registration process is fairly easy which creates oppotunities for fake sellers. Another notable disadvantage is that even though books have been used the prices are overly high which may discourage lot of buyers. 

\subsubsection{bookswap.lk}
BookSwap.lk is free online platform for exchange used books or sell books free online. You can buy second hand books, text books or used books by institutions. Even though they have put up an extensive collection of books the website is still completed as they haven't specified a payment method. Platform encourages to meet the buyer personally rather than online transactions which might not be appealing for some customers. 

\newpage
\section{Material and Methods}
\subsection{Brief Description of Proposed System Design}
Explain the proposed system design briefly.

\newpage
\section{Expected Results}
Discuss the expected results of your research.

\newpage
\section{Timeline of the Research}
Provide a timeline for your research project.

% Keep the numbered references
\newpage
\section{References}
\begin{thebibliography}{9}
% Your references go here
\end{thebibliography}

\end{document}
