\documentclass[english,10pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{babel}
\title{Functionality Of The Book Exchange System}
\author{Ashma Sandeepa}
\begin{document}
	\maketitle
	\large{Through this system, individuals can exchange their books with someone else and also buy new books from bookstores registered in the system.}
	
	\section*{1. Features}
		\subsection*{1.1 User Authentication and Authorization}
			\begin{itemize}
			\item User can Loging and sign-up using username, password and email or Facebook.
			\item Bookshops can register by entering the following information: shop name, contact information (Address, Phone Number, Email Address), owner/manager information (Name, Contact Number, Email Address), hours of operation, shop description, shop policies (Terms and Conditions, Return Policy), inventory quantity, social media links, and website URL.
			\end{itemize}
		\subsection*{1.2 Book Listing}
			\begin{itemize}
				\item User and Book shop can list books manually or using barcode.
			\end{itemize}
		\subsection*{1.3 Search and Filter}
			\begin{itemize}
				\item Use Title, Author, Genre/Category, ISBN, Condition, Price Range, Location/Distance, Language as a filter to better search.
			\end{itemize}
		\subsection*{1.4 Book Details}
			\begin{itemize}
			\item User click the book picture then show all the detail relevant to the book.
			\end{itemize}
		\subsection*{1.5 User Profiles}
			\begin{itemize}
				\item User profile shows user purchased books (only show to profile owner) and user’s basic detail.
				\item Book shop profile show all the details of the shop buyer should know.
			\end{itemize}
		\subsection*{1.6 Notifications}
			\begin{itemize}
				\item If user add a book to favourite list it notifies to that book owner or book shop. 
				\item If the book is not available to the user, the system will notify the user if the book is listed in the system within one week.
			\end{itemize}
		\subsection*{1.7 Transactions and Payments}
		
		
	\section*{2. Technology Stack}
		\subsection*{2.1 Front-end}	
			\begin{itemize}
				\item design UI using figma. 
				\item Use React for Frant end coding.
			\end{itemize}
		\subsection*{2.2 Backend}
			\begin{itemize}
				\item Use Node.js for Back-end coding. 
			\end{itemize}
		\subsection*{2.3 Database}
			\begin{itemize}
				\item Use MongoDB for create Database. 
			\end{itemize}
		\subsection*{2.4 External APIs}
			\begin{itemize}
				\item Payment Gateway API (Stripe, PayPal): Allows secure online payments for book transactions
				\item Geolocation API (Google Maps API): Helps users locate nearby book sellers or potential exchange partners.
				\item Email Notifications API (SendGrid, Mailgun): Enables automated email notifications for events like registration confirmation, message alerts, and more.
				\item Search and Recommendations API (Algolia, Elasticsearch): Enhances the search and filtering capabilities for books.
				\item Social Media Integration API (Facebook): Enables users to log in or share listings via their social media accounts
				\item ISBN Database API (Open Library API): Allows for easy retrieval of book information based on ISBN numbers.
				\item Image Recognition API (Google Cloud Vision, Amazon Rekognition): Helps users quickly upload book covers by recognizing images.
				\item Social Sharing API (AddThis, ShareThis): Allows users to easily share book listings on various social media platforms.
			\end{itemize}
		\subsection*{2.5 Hosting and Deployment}
		\subsection*{2.6 Use Decentralized servers for storing book list for more secure.}
		
	\section*{3. Security}
		\subsection*{3.1 encrypt and store users and sellers sensitive  data}
		\subsection*{3.2 Use two factor authentication for logging.}
			
		
			
			
		
		
			
	
\end{document}