\documentclass{article}
\usepackage{apacite}

\begin{document}

\section*{References}

\begin{enumerate}
    \item Robillard, M. P., Walker, R. J., \& Zimmermann, T. (2010). Recommendation systems for software engineering. \textit{IEEE Software}, 27(4), 80-86.
    \item Koren, Y., Bell, R. M., \& Volinsky, C. (2009). Matrix factorization techniques for recommender systems. \textit{IEEE Computer}, 42(8), 30-37.
    \item Raghothaman, M., Wei, Y., \& Hamadi, Y. (2016). SWIM: synthesizing what i mean: code search and idiomatic snippet synthesis. In \textit{Proceedings of the 38th International Conference on Software Engineering (ICSE)} (pp. 357-367).
    \item OpenAI. (2023). GPT-3 Documentation.
    \item Goodreads API. (2023). Goodreads API Documentation.
    \item TensorFlow. (2022). TensorFlow Documentation.
    \item Petrosyan, G., Robillard, M. P., \& Mori, R. D. (2015). Discovering information explaining API types using text classification. In \textit{Proceedings of the 37th IEEE/ACM International Conference on Software Engineering (ICSE)} (Vol. 1, pp. 869-879).
    \item Zhong, H., Xie, T., Zhang, L., Pei, J., \& Mei, H. (2009). MAPO: mining and recommending API usage patterns. In \textit{ECOOP 2009-Object-Oriented Programming 23rd European Conference} (pp. 318-343).
    \item Nguyen, A. T., Nguyen, T. T., Nguyen, H. A., Tamrawi, A., Nguyen, H. V., \& Al-Kofahi, J. M. (2012). Graph-based pattern-oriented context-sensitive source code completion. In \textit{Proceedings of the 34th International Conference on Software Engineering (ICSE)} (pp. 69-79).
    \item Ye, D., Xing, Z., Foo, C. Y., Li, J., \& Kapre, N. (2016). Learning to extract API mentions from informal natural language discussions. In \textit{Proceedings of the 2016 IEEE International Conference on Software Maintenance and Evolution (ICSME)} (pp. 389-399).
    \item Treude, C., \& Robillard, M. P. (2016). Augmenting API documentation with insights from stack overflow. In \textit{Proceedings of the 38th International Conference on Software Engineering (ICSE)} (pp. 392-403).
    \item Hussain, Y., Huang, Z., Zhou, Y., \& Wang, S. (2020). Deep transfer learning for source code modeling. \textit{International Journal of Software Engineering and Knowledge Engineering}, 30(5), 649-668.
    \item Huang, Q., Xia, X., Xing, Z., Lo, D., \& Wang, X. (2018). API method recommendation without worrying about the task-API knowledge gap. In \textit{Proceedings of the 33rd ACM/IEEE International Conference on Automated Software Engineering (ASE)} (pp. 293-304).
    \item Zhou, Y., Yang, X., Chen, T., Huang, Z., Ma, X., \& Gall, H. C. (2021). Boosting API recommendation with implicit feedback. \textit{IEEE Transactions on Software Engineering}.
\end{enumerate}

\end{document}
