\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\title{Requirement Analysis}
\author{Your Name}
\date{\today}

\begin{document}

\maketitle

\section{Functional Requirements}
\begin{enumerate}[label=\arabic*.]
    \item User Registration and Authentication: Users should be able to register and authenticate themselves securely to access the system.
    \item Book Listing: Sellers should be able to list their used books for sale, providing details such as title, author, condition, price, and description.
    \item Book Search and Discovery: Users should be able to search for books based on various criteria, including title, author, genre, and keywords. The system should provide personalized recommendations based on user preferences.
    \item Transaction Management: The system should facilitate secure transactions between buyers and sellers, ensuring transparency and traceability through blockchain integration.
    \item User Reviews and Ratings: Users should be able to leave reviews and ratings for sellers and books, contributing to transparency and trust in the marketplace.
\end{enumerate}

\section{Non-Functional Requirements}
\begin{enumerate}[label=\arabic*.]
    \item Performance: The system should be responsive and scalable to handle concurrent user requests and large volumes of data.
    \item Usability: The user interface should be intuitive and user-friendly, catering to users with varying levels of technical expertise.
    \item Reliability: The system should be reliable, with minimal downtime and robust error handling mechanisms.
    \item Scalability: The system architecture should be designed to scale horizontally to accommodate increasing user demand and data growth.
    \item Interoperability: Integration with external systems and services should be seamless, allowing for interoperability with existing platforms and databases.
    \item Security: Implementation of strong encryption, authentication, and authorization mechanisms to protect user data and prevent unauthorized access or tampering.
    \item Compliance: Ensuring compliance with relevant regulatory requirements, such as data protection laws and financial regulations.
    \item Performance Monitoring and Logging: Implementing monitoring and logging functionalities to track system performance, diagnose issues, and facilitate troubleshooting.
    \item Accessibility: Ensuring that the system is accessible to users with disabilities, conforming to accessibility standards and guidelines.
    \item Documentation: Comprehensive documentation should be provided for system architecture, APIs, and user guides to facilitate development, integration, and usage.
\end{enumerate}

\end{document}
